Statistical Searches for Microlensing Events in Large, Non-Uniformly Sampled Time-Domain Surveys: A Test Using Palomar Transient Factory Data

### 2013-10-07 text/paper/ms.tex
add percentages for each step, how many light curves removed

\section{Searching for events in the full PTF dataset}\label{sec:search}
To identify candidate microlensing events in the $1.1\times10^9$ light curves with $>$10 $R$-band observations, we:
%We apply the 1\% FPR cut to the 2097 PTF fields ($\sim$15,224 deg$^2$) with $>$10 $R$-band observations using the variability index $\eta$. Our procedure is as follows:
\begin{enumerate}
	\item select a field from the 2097 fields with $>$10 good $R$-band observations and run Monte Carlo simulations to compute the 1\% FPR limiting values for $\eta$, $\Delta \chi^2$, and $J$ for that field;
	\item compute $\eta$ for all the light curves in the field, and select the light curves that pass the quality cut described in Section~\ref{sec:detection_eff} and the FPR cut determined from the Monte Carlo simulations;
	\item fit a microlensing event model and subtract the model, then recompute $\eta$ for all the selected light curves;
	\item reject the light curves for which the new value of $\eta$ still passes the cut\footnote{These are probably periodic variables.};
	\item retain any remaining light curves for further inspection.
\end{enumerate}
% Turn this into a table, with number of objects left over after each cut?

This procedure identifies 2377 candidates from among the initial sample of $1.1\times10^9$ light curves. We search SIMBAD\footnote{This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France.} and remove any candidate among these with a known extragalactic counterpart within 10\asec. For those in the SDSS footprint, we use Data Release 7 photometry \citep{DR7paper} to identify candidate quasars \citep[using the cuts described in][]{richards02} and examine the SDSS images \citep{sdss_images} to remove extended objects. Removing extragalactic objects in this manner from our candidate list reduces contamination by, e.g., supernovae.

@@

%\bigskip
%\setlength{\baselineskip}{0.6\baselineskip}
%\bibliography{references_5}
%\bibliography{references_3}
%\setlength{\baselineskip}{1.667\baselineskip}

@@

\bibitem[{{Abazajian} {et~al.}(2009)}]{DR7paper}
{Abazajian}, K.~N., {et~al.} 2009, \apjs, 182, 543

@@

>>>>

\section{Searching for events in the full PTF dataset}\label{sec:search}
To identify candidate microlensing events in the $1.1\times10^9$ light curves with $>$10 $R$-band observations, we:
%We apply the 1\% FPR cut to the 2097 PTF fields ($\sim$15,224 deg$^2$) with $>$10 $R$-band observations using the variability index $\eta$. Our procedure is as follows:
\begin{enumerate}
	\item select a field from the 2097 fields with $>$10 good $R$-band observations and run Monte Carlo simulations to compute the 1\% FPR limiting values for $\eta$, $\Delta \chi^2$, and $J$ for that field;
	\item compute $\eta$ for all the light curves in the field, and select the light curves that pass the quality cut described in Section~\ref{sec:detection_eff} ($\sim$10\%) and the FPR cut determined from the Monte Carlo simulations ($\sim$0.1-0.5\%);
	\item for fields with SDSS coverage, we use Data Release 9 photometry \citep{dr9paper} to remove sources typed as Galaxy or QSO (using \texttt{objc\_type}\footnote{http://www.sdss3.org/dr9/algorithms/classify.php}) and flag candidate quasars \citep[using the cuts described in][]{richards02} ($\sim$10\%);
	\item fit a microlensing event model and subtract the model, then recompute $\eta$ for all the selected light curves;
	\item reject the light curves for which the new value of $\eta$ still passes the cut\footnote{These are probably periodic variables.} ($\sim$5-10\%);
	\item retain any remaining light curves for further inspection.
\end{enumerate}
% Turn this into a table, with number of objects left over after each cut?

This procedure identifies 2377 candidates from among the initial sample of $1.1\times10^9$ light curves. We search SIMBAD\footnote{This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France.} and remove any candidate among these with a known extragalactic counterpart within 10\asec. For those in the SDSS footprint, we examine the SDSS images \citep{sdss_images} to remove extended objects. Removing extragalactic objects in this manner from our candidate list reduces contamination by, e.g., supernovae.

@@

%\bigskip
%\setlength{\baselineskip}{0.6\baselineskip}
%\bibliography{references_3}
%\setlength{\baselineskip}{1.667\baselineskip}

@@

@@

\bibitem[{{Ahn} {et~al.}(2012){Ahn}, {Alexandroff}, {Allende Prieto},
  {Anderson}, {Anderton}, {Andrews}, {Aubourg}, {Bailey}, {Balbinot}, {Barnes},
  \& et~al.}]{dr9paper}
{Ahn}, C.~P., {Alexandroff}, R., {Allende Prieto}, C., {et~al.} 2012, \apjs,
  203, 21
